% Target: 20ish pages total; 13 pages of text, 7 pages of images
\chapter{Approach}
In this chapter we describe our chosen approach for improving the performance of network bound workloads in serverless edge computing environments. We start by explaining our considerations when developing our approach in the context of a serverless edge computing system, and showing in what way our solution changes the system. From there we go into detail about how the load balancing mechanism of our solution works, how it is different from the currently employed methods, and how the choices made in regard to the load balancing method inform other parts of the proposed approach.
Lastly we go into our approach to scaling and scheduling load balancers among the nodes present in the serverless edge computing system. We make use of osmotic scaling and scheduling, a method previously outlined in existing literature. Using this idea of osmotic scaling and scheduling, we provide a concrete implementation of such an approach for placing and deciding on the number of load balancers in the system. The implementation is designed with current state of the art systems such as Kubernetes as the basis, and can thus be used as a reference implementation for use outside of a simulation context. The approach also addresses the challenges of edge computing environments that make current approaches, developed with the cloud in mind, unsuitable. Specifically our approach addresses issues of location awareness, device and network heterogeneity, and dynamically changing workload conditions.
\input{chapters/4_Approach/1_general}
\input{chapters/4_Approach/2_load_balancer}
\input{chapters/4_Approach/3_osmotic}